---
title: "au_tmdl_intersect_tool"
author: "Jordan Hoehnen"
date: '2023-03-20'
output: pdf_document
---

#Libraries
```{r}
arc.check_product()
library(arcgisbinding)
library(sf)
library(sp)
library(tidyverse)
library(ROracle)
library(rgdal)
library(tidyr)
```

##Settings 
#Causes are the analyte's causing water impairments 
```{r}
options(scipen = 9)

causes = c("Sediment/Total Suspended Solids",
           "Total Phosphorus")

listed_waters = c("303d Listed", "TMDL Development")
```

#Insert username and password for DNR_SECPRD.WORLD
```{r}
usr = rstudioapi::askForPassword(prompt="Please enter username")
pwd = rstudioapi::askForPassword()
```

#This code makes  tables comma delimited
```{r}
com_delim = function(df, col) {
  out = df %>%
    # st_drop_geometry() %>%
    .[[col]] %>%
    str_split(., ",") %>%
    unlist(.) %>%
    str_trim() %>%
    unique() %>%
    sort() %>%
    paste(., collapse=", ")
  return(out)
}
```

#"info table" -- contains waterbody name, waters ID, WBIC, County, Start & End mile, source category, impairment indicator, pollutant, TP Criterion, Basin, TMDL Subbasin
```{r}
con = dbConnect(drv=Oracle(), dbname="dnr_secprd.world", username=usr, password=pwd)
info_tbl = dbGetQuery(con, "select OFFICIAL_NAME, WBIC, ASSESSMENT_UNIT_SEQ_NO, COUNTY_NAME, START_MILE_NO, END_MILE_NO, IMPAIRED_WATERS_CATEGORY,
                      IMPAIRMENT, POLLUTANT, WATERSHED_NAME, TMDL_ID, STATUS_CODE from W23321.WT_IMPAIREDWATERS_CNTY_LIST_MV") %>%
  left_join(
      dbGetQuery(con, "SELECT ASSESSMENT_UNIT_SEQ_NO, EPA_ID305B FROM W23321.WT_ASSESSMENT_UNIT"),
      by="ASSESSMENT_UNIT_SEQ_NO") %>%
  filter(POLLUTANT %in% causes)%>%
  filter(STATUS_CODE %in% listed_waters)
dbDisconnect(con)
```

#TP Criteria for lakes/imoundments and rivers/streams
```{r}
#Lakes/Impoundments TP Criteria
con = dbConnect(drv=Oracle(), dbname="dnr_secprd.world", username=usr, password=pwd)
lakes_tp_criteria = dbGetQuery(con, "SELECT SNAPSHOT_ID, ASSESSMENT_UNIT_SEQ_NO, TP_THRESHHOLD FROM W23321.WT_LAKE_TP_STATION_SUMMARY_VX")
lakes_tp_criteria_drop <- lakes_tp_criteria[duplicated(lakes_tp_criteria$ASSESSMENT_UNIT_SEQ_NO), ]
length(unique(lakes_tp_criteria_drop$ASSESSMENT_UNIT_SEQ_NO))
length(unique(lakes_tp_criteria_drop$ASSESSMENT_UNIT_SEQ_NO)) == nrow(lakes_tp_criteria_drop)
dbDisconnect(con)

#Stream/River TP Criteria
con = dbConnect(drv=Oracle(), dbname="dnr_secprd.world", username=usr, password=pwd)
stream_tp_criteria = dbGetQuery(con, "SELECT ASSESSMENT_UNIT_SEQ_NO, TP_THRESHHOLD_100_FLAG FROM W23321.WT_ASSESSMENT_UNIT")
dbDisconnect(con)
stream_tp_criteria <- stream_tp_criteria %>%
  mutate(tp_criteria = case_when(TP_THRESHHOLD_100_FLAG == 'Y' ~ '100',
                                 TP_THRESHHOLD_100_FLAG == 'N' ~ '75'))
stream_tp_criteria = select(stream_tp_criteria, -2)
```

## Run this code to get subbasins file for the project area
#Insert corresponding Plan_Seq_No for the TMDL or project area of interest 
```{r}
tmdl_subbasins = arc.open("C:/Users/hoehnj/Documents/ArcGIS/Projects/generic_work/HOEHNJ[DNRWQRP].sde/DNRWQRP.WT_PLAN_TMDL_SUBBASINS_AR")
tmdl_subbasins = arc.select(tmdl_subbasins, where_clause = "PLAN_SEQ_NO = 153881362")
tmdl_subbasins_sf = arc.data2sf(tmdl_subbasins)
```

#Lakes/Impoundments
```{r}
#Lakes variable: Route correct path to DNR_SDE.SDE 
au_lakes = arc.open("C:/Users/hoehnj/Documents/ArcGIS/Projects/generic_work/dnr_sde.world.sde/W23321.WT_ASSESSMENT_UNIT_DATA_24K/W23321.WT_ASSESSMENT_UNIT_AR_24K")
au_lakes = arc.select(au_lakes)
au_lakes_sf = arc.data2sf(au_lakes) %>%
  left_join(info_tbl, by=c("ASSESSMENT_UNIT_SEQ_NO"="ASSESSMENT_UNIT_SEQ_NO")) %>%
  left_join(lakes_tp_criteria, by=c("ASSESSMENT_UNIT_SEQ_NO"="ASSESSMENT_UNIT_SEQ_NO")) %>%
  filter(STATUS_CODE %in% listed_waters)

#Intersection between lakes and TMDL subbasins
lakes_intersect <- st_intersection(au_lakes_sf, tmdl_subbasins_sf) %>% 
  select(OFFICIAL_NAME, ASSESSMENT_UNIT_SEQ_NO, WBIC, COUNTY_NAME, START_MILE_NO, END_MILE_NO,
         IMPAIRED_WATERS_CATEGORY, IMPAIRMENT, POLLUTANT, WATERSHED_NAME, TMDL_ID, EPA_ID305B, TP_THRESHHOLD, SUBBASIN) %>%
  group_by(OFFICIAL_NAME, ASSESSMENT_UNIT_SEQ_NO, WBIC, COUNTY_NAME, START_MILE_NO, END_MILE_NO, WATERSHED_NAME, TP_THRESHHOLD, TMDL_ID, EPA_ID305B, IMPAIRED_WATERS_CATEGORY) %>%
  nest() %>%
  mutate(
    IMPAIRMENT=lapply(data, com_delim, col="IMPAIRMENT"),
    POLLUTANT=lapply(data, com_delim, col="POLLUTANT"),
    TMDL_Subbasin=lapply(data, com_delim, col="SUBBASIN"),
  ) %>%
  ungroup()

impaired_lakes <- filter(lakes_intersect[!duplicated(lakes_intersect$WBIC),])
impaired_lakes <- select(impaired_lakes, -12)
impaired_lakes <- apply(impaired_lakes,2,as.character)
```

#Write lakes impairments table to csv. 
```{r}
write.csv(impaired_lakes, "nel_impaired_lakes.csv", row.names = FALSE)
```


#Rivers/Streams
```{r}
#Streams variable: Route correct path to DNR_SDE.SDE  
au_streams = arc.open("C:/Users/hoehnj/Documents/ArcGIS/Projects/generic_work/dnr_sde.world.sde/W23321.WT_ASSESSMENT_UNIT_DATA_24K/W23321.WT_ASSESSMENT_UNIT_LN_24K")
au_streams = arc.select(au_streams)
au_streams_sf = arc.data2sf(au_streams) %>%
  left_join(info_tbl, by=c("ASSESSMENT_UNIT_SEQ_NO"="ASSESSMENT_UNIT_SEQ_NO")) %>%
  left_join(stream_tp_criteria, by=c("ASSESSMENT_UNIT_SEQ_NO"="ASSESSMENT_UNIT_SEQ_NO")) %>%
  filter(STATUS_CODE %in% listed_waters)

#Intersection between streams and subbasins
streams_intersect <- st_intersection(au_streams_sf, tmdl_subbasins_sf) %>% 
  select(OFFICIAL_NAME, ASSESSMENT_UNIT_SEQ_NO, WBIC, COUNTY_NAME, START_MILE_NO, END_MILE_NO, IMPAIRED_WATERS_CATEGORY, IMPAIRMENT,
         POLLUTANT, WATERSHED_NAME, TMDL_ID, EPA_ID305B, STATUS_CODE, SUBBASIN, tp_criteria) %>%
  mutate(LEN_miles=as.numeric(st_length(geom)*0.000621371)) %>%
  group_by(ASSESSMENT_UNIT_SEQ_NO) %>%
  mutate(AU_LEN_FRAC = LEN_miles / sum(LEN_miles)) %>%
  arrange(ASSESSMENT_UNIT_SEQ_NO, SUBBASIN)


impaired_streams <- streams_intersect[!duplicated(streams_intersect$geom),] %>%
  filter(AU_LEN_FRAC > 0.000000004) %>%
  group_by(OFFICIAL_NAME, ASSESSMENT_UNIT_SEQ_NO, WBIC, COUNTY_NAME, START_MILE_NO, END_MILE_NO,
           IMPAIRED_WATERS_CATEGORY,  WATERSHED_NAME, TMDL_ID, EPA_ID305B, tp_criteria) %>%
  nest() %>%
  mutate(
    IMPAIRMENT=lapply(data, com_delim, col="IMPAIRMENT"),
    POLLUTANT=lapply(data, com_delim, col="POLLUTANT"),
    TMDL_Subbasin=lapply(data, com_delim, col="SUBBASIN"),) %>%
  ungroup() 
impaired_streams = select(impaired_streams, -12)

impaired_streams <- apply(impaired_streams,2,as.character)
```

#Write stream impairments table to csv. 
```{r}
write.csv(impaired_streams, "nel_impaired_streams.csv", row.names = FALSE)
```
